---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# Habitat modeling

Data is held in a private google drive folder. If you have access to the folder, open analysis/data/raw_data/load_new_data.R and follow the directions. Once the raw data is loaded open analysis/procedure/habitatmodel.R. You will need to have BlueBRIDGE access to the [https://i-marine.d4science.org/group/stockassessment](BlueBRIDGE Stock Assessment VRE) to run the analysis on the BlueBRIDGE e-infrastructure. Once you have access, you will be asked to provide your login and token when you run the analysis.


### Citation

Please cite this compendium as:

> Authors, (`r format(Sys.Date(), "%Y")`). _Title of compendium_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

### Installation

You can install habitatmodel from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("slarge/HabMod")
```

### Licenses

**Text and figures:**  [CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/)

**Code:** See the [DESCRIPTION](DESCRIPTION) file

$\textbf{Data:}$ [CC-0](http://creativecommons.org/publicdomain/zero/1.0/) attribution requested in reuse

### Contributions

We welcome contributions from everyone. Before you get started, please see our [contributor guidelines](CONTRIBUTING.md). Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.
