---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# Introduction to the package

This project was created with the [`rrrpkg` package](https://github.com/ropensci/rrrpkg) and is intended to serve as a [Research Compendium](https://github.com/ropensci/rrrpkg). The easiest way to get your hands dirty and explore data and run the analysis is to clone the [HabMod github repository](https://github.com/slarge/HabMod) (instructions on how to clone and general github/Rstudio knowledge can be found at [happygitwithr.com](http://happygitwithr.com/rstudio-git-github.html#clone-the-new-github-repository-to-your-computer-via-rstudio) -- replace 'myrepo' with 'slarge/HabMod'). Once you have the project cloned, you will need to add a few functions necessary to load data. "Load all" using the keyboard shortcut ctrl+shift+L, which will load these functions into the current Global Environment.

Data is held in a private google drive folder. If you have access to the folder, open the analysis/data/raw_data/load_new_data.R script and follow the instructions to download the data. The intention, here, is to copy data from the google drive folder into the R package directory structure in a consistent way to facilitate batch processessing the data in subsequent analyses.

# Habitat modeling
Once data are loaded using the analysis/data/raw_data/load_new_data.R script, you can get started with the analysis. Load the analysis/procedure/xgboost_habitat.R script. This script loads the raw data and adds a presence/absence vector for each species and then models presence/absence habitat and biomass habitat. Fitting with the xgboost algorithm requires a few steps. First, a few hyperparameters need to be tuned, which is done using a Bayesian optimization procedure. Next, the model is tuned.  

### Citation

Please cite this compendium as:

> Large, S and Friedland, K (`r format(Sys.Date(), "%Y")`). _NEUS Habitat Modeling_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

### Installation

You can install habitatmodel from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("slarge/HabMod")
```

### Licenses

**Text and figures:**  [CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/)

**Code:** See the [DESCRIPTION](DESCRIPTION) file

$\textbf{Data:}$ [CC-0](http://creativecommons.org/publicdomain/zero/1.0/) attribution requested in reuse

### Contributions

We welcome contributions from everyone. Before you get started, please see our [contributor guidelines](CONTRIBUTING.md). Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.
